biclaR: Estimating the socio-environmental impacts of car substitution by bicycle and public transit using open tools

### 2023-10-10 paper/PaperTRA/PaperTRA.Rmd
update to-do
minor updates
there are some things that we will improve in the other paper

<!-- TODO: -->
<!-- see where we can cut to 1 less paragraph -->
<!-- should we ignore the social benefits component? and only estimate and add the environmental ones? or estimate the car to tp transfer Social benefits? maybe to the next paper? -->

@@

Emissions were estimated for the following atmospheric pollutants: CO~2~eq, CO, PM10, NOx, and VOC.
In particular, for the urban train and tram -- with 100% electric traction -- only CO~2~eq emissions were considered (resulting from the production of electricity, considering a "well-to-tank" approach), since the other pollutants are not emitted locally.

@@

knitr::kable(summary1,
      digits = 0,
      format.args = list(big.mark = " "),
      col.names = c("Target", "Routing", "Total trips",
                    "Baseline Cycling + PT", "Potencial Cycling + PT",
                    "Avoided CO2eq (ton/yr)", "SE Benefits for 10 years (thousand €)"),
      caption = "\\label{summary1}Summary of the cycling potencial of intermodality scenario.",
      format="latex",
      booktabs = TRUE) |> 
  kableExtra::column_spec(column = c(4:7), width = "6em")

@@

<!-- separate the Socio impacts from the Environemtal ones? It shouldn't be ok to sum them -->
Shifting from car to cycling + PT can reduce annual CO~2~eq emissions by 14,000 to 36,000 tons per year, 
and the 10-year socio-environmental benefits account for €235 million to €620 million, depending on the cycling targets.

>>>>

<!-- TODO: -->
<!-- check if HEAT estimates remain the same (the tool is not working atm) -->
<!-- should we ignore the social benefits component? and only estimate and add the environmental ones? or estimate the car to tp transfer Social benefits? maybe to the next paper? -->

@@

Emissions were estimated for the following atmospheric pollutants: CO, PM10, NOx, and VOC; and for the main green house gases: CO~2, CH~4, and N~2~O, converted in CO~2~eq.
In particular, for the urban train and tram -- with 100% electric traction -- only CO~2~eq emissions were considered (resulting from the production of electricity, considering a "well-to-tank" approach), since the other pollutants are not emitted locally.

@@

knitr::kable(summary1,
      digits = 0,
      format.args = list(big.mark = " "),
      col.names = c("Target", "Routing", "Total trips",
                    "Baseline Cycling + PT", "Potencial Cycling + PT",
                    "Avoided CO2eq (ton/yr)", "SE Benefits for 10 years (thousand €)"),
      caption = "\\label{summary1}Summary of the cycling potencial of intermodality scenario and its socio-environmental benefits for the cycling legs.",
      format="latex",
      booktabs = TRUE) |> 
  kableExtra::column_spec(column = c(4:7), width = "6em")

@@

<!-- FOR OTHER PAPER: separate the Socio impacts from the Environmental ones? It shouldn't be ok to sum them -->
Shifting from car to cycling + PT can reduce annual CO~2~eq emissions by 14,000 to 36,000 tons per year, 
and the 10-year socio-environmental benefits account for €235 million to €620 million, depending on the cycling targets.
